Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
cleaned up last paragraph of CO correction discussion

Unfortunately, the CO maps at $6.1'$ are rather noisy,
and the vast majority of the sky has completely negligible CO emission. Thus,
in order to avoid adding unnecessary noise outside of molecular cloud complexes
and at high latitudes, we have zeroed out low-signal regions of the CO Type 3
map. We identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$
 km/s, where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ 
FWHM. This cut results in 90\% of the sky being unaffected by the CO 
correction, particularly the vast majority of the high Galactic latitude sky.

>>>>

Unfortunately, the Type 3 CO map at $6.1'$ FWHM is rather noisy, and the vast
 majority of the sky has completely negligible CO emission. Thus, in order to 
avoid adding unnecessary noise outside of molecular cloud complexes and at high
 latitudes, we have zeroed out low-signal regions of the Type 3 CO map. We 
identify  low-signal regions as those with $\mathcal{I}_3$$<$1 K$_{RJ}$ km/s, 
where $\mathcal{I}_3$ is the Type 3 CO map smoothed to 0.25$^{\circ}$ FWHM. As 
a result of this cut, 90\% of the sky remains unaffected by our CO correction, 
particularly the vast majority of the high Galactic latitude sky.
